simon_test_loop

### 2019-03-21 src/stack_test.Rmd
creating aic + summary table of aic and auc at different regularization values

for (td in 1:nrow(unlayer)){
  temp_depth <- raster(unlayer$temp_depth[td])
  crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(temp_depth) <- "temp_depth"
  temp_depth <- projectRaster(temp_depth, aea)
  chl_surface <- raster(unlayer$chl_surface[td])
  crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(chl_surface) <- "chl_surface"
  chl_surface <- projectRaster(chl_surface, aea)
  o2_depth <- raster(unlayer$o2_depth[td])
  crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(o2_depth) <- "o2_depth"
  o2_depth <- projectRaster(o2_depth, aea)
  salinity_depth <- raster(unlayer$salinity_depth[td])
  crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(salinity_depth) <- "salinity_depth"
  salinity_depth <- projectRaster(salinity_depth, aea)
  nao_sample <- raster(unlayer$nao_sample[td])
  crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(nao_sample) <- "nao_sample"
  nao_sample <- projectRaster(nao_sample, aea)
  nao_winter <- raster(unlayer$nao_winter[td])
  crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
  names(nao_winter) <- "nao_winter"
  nao_winter <- projectRaster(nao_winter, aea)
  stackn <- unlayer$stackname[td]
  test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  #stackSave(test,unlayer$stackname[td])
  pred <- predict(mod1, test, file = paste0("../output/maxentpredict/", stackn), overwrite=TRUE) 
  paste("maxplot_", stackn, ".png", sep = "") # to automatically save the plot to a png AND show it inline
  preplot <- plot(pred, png(paste0("../output/maxentpredict/", stackn, ".png")))
  dev.off() # stops automatic saving of the plot to a png
}

@@

@@

@@

>>>>

for (td in 1:nrow(unlayer)){
  temp_depth <- raster(unlayer$temp_depth[td])
  crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(temp_depth) <- "temp_depth"
  temp_depth <- projectRaster(temp_depth, aea)
  chl_surface <- raster(unlayer$chl_surface[td])
  crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(chl_surface) <- "chl_surface"
  chl_surface <- projectRaster(chl_surface, aea)
  o2_depth <- raster(unlayer$o2_depth[td])
  crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(o2_depth) <- "o2_depth"
  o2_depth <- projectRaster(o2_depth, aea)
  salinity_depth <- raster(unlayer$salinity_depth[td])
  crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(salinity_depth) <- "salinity_depth"
  salinity_depth <- projectRaster(salinity_depth, aea)
  nao_sample <- raster(unlayer$nao_sample[td])
  crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(nao_sample) <- "nao_sample"
  nao_sample <- projectRaster(nao_sample, aea)
  nao_winter <- raster(unlayer$nao_winter[td])
  crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
  names(nao_winter) <- "nao_winter"
  nao_winter <- projectRaster(nao_winter, aea)
  stackn <- unlayer$stackname[td]
  test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  #stackSave(test,unlayer$stackname[td])
  pred <- predict(mod1, test, file = paste0("../output/maxentpredict/", stackn, ".asc"), overwrite=TRUE) #sam you just added.asc but have not tested
  paste("maxplot_", stackn, ".png", sep = "") # to automatically save the plot to a png AND show it inline
  preplot <- plot(pred, png(paste0("../output/maxentpredict/", stackn, ".png")))
  dev.off() # stops automatic saving of the plot to a png
}

@@

#--------------------------

#play with test and training data - note will want to give your own file in the 'real model'
mod9 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30")) 
mod9

pre9 <- predict(mod9, test, args='outputformat=logistic' ) 
preplot9 <- plot(pre9)
preplot9

#ok this works but doesnt show much difference in the map

#run a model with all years data and project as you have been 
presaball <- read.csv("../output/bio/presab_10k.csv", header = TRUE)
subpresaball <- subset(presaball, select = c(occurrence, temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter))
subpaall <- subpresaball$occurrence
subpresaball <- subset(subpresaball, select = -c(occurrence))

mod10 <- maxent(x = subpresaball, p = subpaall, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30")) 
mod10

pre10 <- predict(mod10, test, args='outputformat=logistic' ) 
preplot10 <- plot(pre10)
preplot10

# well this makes a terrible mess... the habitat is predicted to be everywhere and the response curves a mess! Was just curious.

#--------------------

#back to fiddling

mod11 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "replicatetype=boo", "replicates=10")) 
mod11

pre11 <- predict(mod11, test, args='outputformat=logistic' ) 
preplot11 <- plot(pre11)
preplot11

#-------------------

#aic fiddling

betamval <- 0.25
mod9 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=0.25"), path = "../output/maxent/output/mod9foraic") 
mod9

pre9 <- predict(mod9, test, args='outputformat=logistic' ) 
preplot9 <- plot(pre9)
preplot9

#now based on glover-kapfer pdf with excel manual.... lets try automate some of this..

#count number of non-zero coefficinets, excluding the final four rows
coefile <- read.csv("../output/maxent/output/mod9foraic/species.lambdas", header = FALSE)
coefile <- head(coefile, -4)
coefile2 <- subset(coefile, V2 > 0 | V2 < 0)
nocoeff <- nrow(coefile2)

#no presences used in model (less those used for testing)
maxresults <- read.csv("../output/maxent/output/mod9foraic/maxentResults.csv", header = TRUE)
notrainingpoints <- maxresults$X.Training.samples
testauc <- maxresults$Test.AUC
trainauc <- maxresults$Training.AUC

#natural log
samplepred <- read.csv("../output/maxent/output/mod9foraic/species_samplePredictions.csv", header = TRUE)
samplepred$nat_log <- log(samplepred$Raw.prediction)
sumsamplepred <- sum(samplepred$nat_log)

AIClist <- read.csv("../data/env/AICcCalculations.csv", header = TRUE)
for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

  }
}

AIClist$AIC <- ((2*AIClist$coefficients)-(2*AIClist$sum.of.logs))
AIClist$AICc <- (-2*(AIClist$sum.of.logs)+((2*AIClist$coefficients)*(AIClist$n/(AIClist$n - AIClist$coefficients-1))))

@@

try changing some of the settings here - paerticularly you want aic
```{r}
VariableSelection(maxent="C:/Users/bunny/Downloads/maxent/maxent.jar", outdir=("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/output"), gridfolder=("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/testgrid"), occurrencelocations= ("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/presence_red.csv"), backgroundlocations= ("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/background_red.csv"), additionalargs="nohinge", contributionthreshold=5, correlationthreshold=0.9, betamultiplier=seq(0.25, 2, 0.25))
```
no you cant - you need to use the grids...

@@

# for mj thing - no points per nafo zone

I previously worked out the area for each nafo zone in arcgis. This caclulates the  number of points per nafo zone

```{r}
allpoints <- read.csv("../output/bio/background/correct_random_files/background_point_na_removal_nona.csv", header = TRUE) #you may want to move the files once you figure out what mess you created..
nafo_points <- count(allpoints, "nafo_zone")
total_points <- sum(nafo_points$freq) #191055 -correct
nafo_points$points_percentage <- (nafo_points$freq/total_points)*100

#combine with the arcgis output...
nafovolume <- read.csv("../data/env/volume_all_nafo.csv", header = TRUE) #note the hudson strait points will be invalid as there is no polygon to calculate volume on. change to NA
nafo_points$volume <- nafovolume$Volume
nafo_points$volume_percentage <- nafovolume$volume_perc

write.csv(nafo_points, file = "../output/env/no_points_per_nafo.csv")
```
